---
title: "oi2142_Homework1"
output: github_document
---

## Attaching packages
```{r setup}
library(tidyverse)
```

## Problem 1: 
Creating a data  frame using Tibble

    
```{r dataframe_tibble, echo=FALSE}
  homework1_df = tibble (
    vec_numeric = rnorm(10)
,    vec_char = c("Wendy", "Kevin", "Fred", "Jeff", "Leslie", "Jen", "Michelle", "Emily", "Jake", "Sam"),
    vec_logical = c("TRUE", "TRUE", "TRUE", "FALSE", "TRUE", "TRUE", "TRUE", "FALSE", "TRUE", "TRUE"),
    vec_factor = factor (c("work", "home", "mobile", "work", "home", "mobile", "work", "home", "mobile", "home")))
```


```{r print tibble, echo=FALSE}
homework1_df
```

## Taking the mean using the pull function 



```{r means using pull}
mean(pull (homework1_df, var = vec_numeric))
mean(pull(homework1_df, var = vec_char))
mean(pull(homework1_df, var = vec_logical))
mean(pull(homework1_df, var = vec_factor))
```

## 
Taking the mean for the numeric variable in the data fram worked, but taking the mean for the logical,  character, and factor did not work.


# Using the as.numeric function to convert variable
  I believe that the as.numeric function worked for vec_factor because this variable has a has 3 different "levels". The numbers assigned are now coded as 1,2, or 3. 
  
  When trying to convert vec_char and vec_logistical, I get a warning message that says "NAs introduced by coercion". #
  
```{r As Numeric Function, eval=FALSE}
x <- as.numeric(pull(homework1_df, vec_factor))
mean(x)

y <- as.numeric(pull(homework1_df, vec_char))
mean(y)

z <- as.numeric(pull(homework1_df, vec_logical))
mean(z)
```

# Problem 2 
  The dataset 'penguins' has 344 observations and 8 variables. Using ncol = 8 and nrow = 344. The variables include:
  
  (3)Species: Adele, Chinstrap, Gentoo
  
  (3)Islands: Biscoe, Dream, Torgersen
  
  Bill length- mm
  
  Bill depth - mm
  
  Flipper length - mm
  
  body mass - g
  
  Sex - M/F
  
  year - 2007 -2009
  
  
  The mean flipper length is 201 mm. 
```{r, opening penguins data}
data("penguins", package = "palmerpenguins")
```

## 
  Plots


```{r Scatterplot, echo=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```


